A systematic search for transiting planets in the \KT\ data

### 2015-02-16 ms.tex
kepler team acknowledgement
typos in FP

Ground-based transit surveys have experienced false-positive rates
well over 50\%.  For example, \citet{Latham:2009} reported eight
eclipsing binaries and one transiting planet among the sample of
transit candidates in one field of the Hungarian Automated Telescope
Network transit search.  In fact, the follow-up process to try to rule
out such astrophysical false positives is a large portion of the
effort that goes into a transit survey
\citep[e.g.,][]{Odonovan:2006,Almenara:2009,Poleski:2010}.

@@

A quick \emph{a priori} estimate of the background blended ecipsing
binary rate serves as a good sanity check.  A query to the TRILEGAL
(TRIdimensional modeL of thE GALaxy, \citet{Girardi:2005}) galaxy
line-of-sight simulation software reveals that the typical density of
field stars along the line of sight to the C1 field is about
$7.8\times 10^{-4}$\,arcsec$^{-2}$.  This gives a probability of about
0.16 that a background star might be blended within a 8\,arcsec radius
(two pixels) from a target star.  Allowing that something close to
$\sim$10\% of stars might host close binary companions within the
period range accessible by this survey, this gives a probability of
0.016 that a blended binary star might be chance-aligned within two
pixels of any given target star.  Noting that the average number of
planets per star with periods less than 30 days is about 0.25
\citep{Fressin:2013}, we can roughly estimate that we expect $<$10\%
of our candidates to be caused by nearby contaminating EBs.  This
estimate suggests that such astrophsycial false positives should be
rare in our sample, consistent with our detection of 2/36 candidates
with clear centroid offsets.

@@

The remaining signals are caused by eclipsing binaries (EBs) with visible
secondary eclipses.
In most cases, the search reports the secondary eclipse as a candidate and in
a few very high signal-to-noise cases, the period reported by the pipeline is
incorrect and multiple candidates correspond to the same transit.
It is important to note, however, that the choices made in the search were
heuristically tuned to find planets, not binaries, so our results are not
complete or exhaustive, especially at short orbital periods.
There are other methods specifically tuned to find EBs in \KT\
\citep[such as][]{Armstrong:2014, Armstrong:2015} and these catalogs contain
our full sample of EBs and more.

>>>>

Ground-based transit surveys have experienced false-positive rates
well over 50~percent.  For example, \citet{Latham:2009} reported eight
eclipsing binaries and one transiting planet among the sample of
transit candidates in one field of the Hungarian Automated Telescope
Network transit search.  In fact, the follow-up process to try to rule
out such astrophysical false positives is a large portion of the
effort that goes into a transit survey
\citep[e.g.,][]{Odonovan:2006,Almenara:2009,Poleski:2010}.

@@

A quick \emph{a priori} estimate of the background blended eclipsing
binary rate serves as a good sanity check.  A query to the TRILEGAL
(TRIdimensional modeL of thE GALaxy, \citet{Girardi:2005}) galaxy
line-of-sight simulation software reveals that the typical density of
field stars along the line of sight to the C1 field is about
$7.8\times 10^{-4}$\,arcsec$^{-2}$.  This gives a probability of about
0.16 that a background star might be blended within a 8~arcsec radius
(two pixels) from a target star.  Allowing that something close to
$\sim$10\% of stars might host close binary companions within the
period range accessible by this survey, this gives a probability of
0.016 that a blended binary star might be chance-aligned within two
pixels of any given target star.  Noting that the average number of
planets per star with periods less than 30 days is about 0.25
\citep{Fressin:2013}, we can roughly estimate that we expect $<$10\%
of our candidates to be caused by nearby contaminating EBs.  This
estimate suggests that such astrophysical false positives should be
rare in our sample, consistent with our detection of 2/36 candidates
with clear centroid offsets.

@@

The remaining signals are caused by EBs with visible secondary eclipses.
In most cases, the search reports the secondary eclipse as a candidate and in
a few very high signal-to-noise cases, the period reported by the pipeline is
incorrect and multiple candidates correspond to the same transit.
It is important to note, however, that the choices made in the search were
heuristically tuned to find planets, not binaries, so our results are not
complete or exhaustive, especially at short orbital periods.
There are other methods specifically tuned to find EBs in \KT\
\citep[such as][]{Armstrong:2014, Armstrong:2015} and these catalogs contain
our full sample of EBs and more.
